### 2011-11-06 doc/pldi2012/experiments.tex
several figures done - references linked up

\section{Results}

@@

@@

The structure of the circuit simulator was presented in section~\ref{sec:code_example}.  Our implementation uses CUDA to perform the computations on the GPU, and Legion
automatically handles the movement of data between the GPUs' memories and the
system memory, but only when necessary.  In fact, with the help of an
application-specific mapper, it is able to keep much of
the data permanently resident in a given GPU for the entirety of the simulation.
Figure~\ref{sfig:results1:perf} shows the relative speedup as the simulation is
spread over multiple nodes in the cluster.  The size of the circuit
being simulated is not changed as the node count increases.  This is therefore
a demonstration of ``strong scaling''.  Adding a second node to the simulation
speeds it up by 77\%, and with four nodes, the simulation is sped up by a total
of 216\% (i.e. a factor of 3.16x).

@@

@@

The bar chart in figure~\ref{sdif:results2:timers} shows MORE STUFF.

@@

\begin{figure}
  \centering
  \subfigure[Relative Performance]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Processors per Node,ylabel=Normalized Speedup,height=6cm]
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results1:perf}
  }
  \subfigure[Execution Time Breakdown]{
  \begin{tikzpicture}
    \begin{axis}[ybar stacked,bar width=5pt,ylabel=Execution Time (in s)]
    \addplot coordinates {
(1, 25.66)
(2, 32.59)
(3, 35.77)
(4, 36.65)
(5, 25.37)
(6, 31.58)
(7, 34.19)
(8, 36.09)
(9, 25.42)
(10, 31.70)
(11, 34.03)
(12, 35.56)
(13, 28.66)
(14, 32.38)
(15, 33.93)
(16, 37.31)
(17, 26.26)
(18, 34.34)
(19, 35.18)
(20, 36.33)
(21, 31.12)
(22, 36.91)
(23, 38.96)
(24, 41.52)
(25, 31.35)
(26, 45.08)
(27, 46.56)
(28, 47.01)
};
    \addplot coordinates {
(1, 0.01)
(2, 0.75)
(3, 0.89)
(4, 0.93)
(5, 0.01)
(6, 0.96)
(7, 1.26)
(8, 1.34)
(9, 0.01)
(10, 1.49)
(11, 1.53)
(12, 1.98)
(13, 0.02)
(14, 1.67)
(15, 1.60)
(16, 2.45)
(17, 0.02)
(18, 1.59)
(19, 1.86)
(20, 2.23)
(21, 0.03)
(22, 1.74)
(23, 2.06)
(24, 2.18)
(25, 0.05)
(26, 2.31)
(27, 2.12)
(28, 2.32)
};
    \addplot coordinates {
(1, 0.59)
(2, 2.09)
(3, 4.30)
(4, 6.02)
(5, 1.31)
(6, 3.83)
(7, 7.17)
(8, 10.96)
(9, 2.08)
(10, 5.24)
(11, 11.38)
(12, 14.28)
(13, 2.59)
(14, 7.40)
(15, 13.45)
(16, 19.04)
(17, 3.66)
(18, 13.03)
(19, 23.48)
(20, 28.21)
(21, 8.68)
(22, 16.42)
(23, 34.34)
(24, 46.12)
(25, 11.02)
(26, 32.69)
(27, 60.49)
(28, 87.13)
};
    \addplot coordinates {
(1, 0.58)
(2, 4.77)
(3, 4.53)
(4, 4.35)
(5, 1.17)
(6, 2.75)
(7, 2.02)
(8, 2.28)
(9, 0.99)
(10, 1.40)
(11, 1.49)
(12, 1.57)
(13, 2.48)
(14, 1.72)
(15, 1.56)
(16, 1.78)
(17, 1.05)
(18, 1.33)
(19, 1.74)
(20, 1.80)
(21, 1.61)
(22, 1.75)
(23, 1.80)
(24, 1.95)
(25, 1.76)
(26, 2.02)
(27, 2.12)
(28, 2.15)
};
    \addplot coordinates {
(1, 0.00)
(2, 0.00)
(3, 0.00)
(4, 0.00)
(5, 0.00)
(6, 0.00)
(7, 0.00)
(8, 0.00)
(9, 0.00)
(10, 0.00)
(11, 0.00)
(12, 0.00)
(13, 0.00)
(14, 0.00)
(15, 0.00)
(16, 0.00)
(17, 0.00)
(18, 0.00)
(19, 0.00)
(20, 0.00)
(21, 0.00)
(22, 0.00)
(23, 0.00)
(24, 0.00)
(25, 0.00)
(26, 0.00)
(27, 0.00)
(28, 0.00)
};
    \addplot coordinates {
(1, 0.00)
(2, 0.03)
(3, 0.04)
(4, 0.05)
(5, 0.00)
(6, 0.04)
(7, 0.06)
(8, 0.08)
(9, 0.00)
(10, 0.14)
(11, 0.11)
(12, 0.19)
(13, 0.00)
(14, 0.57)
(15, 0.27)
(16, 0.47)
(17, 0.00)
(18, 0.34)
(19, 0.61)
(20, 0.52)
(21, 0.00)
(22, 0.64)
(23, 0.63)
(24, 0.96)
(25, 0.00)
(26, 0.78)
(27, 1.06)
(28, 1.49)
};
    \legend{Application,Memory Copies,High-level,Low-level,Mapper,System}
    \end{axis}
  \end{tikzpicture}
    \label{sfig:results1:timers}
  }
  \caption{Circuit Simulator Results}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[xlabel=Total Processors,ylabel=Normalized Speedup]
    \end{axis}
  \end{tikzpicture}
  \caption{This is a caption}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[xlabel=Total Processors,ylabel=Normalized Speedup,xmin=0,xmax=24]
    \end{axis}
  \end{tikzpicture}
  \caption{This is a caption}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{loglogaxis}[xlabel=Total Processors,ylabel=Normalized Speedup]
    \end{loglogaxis}
  \end{tikzpicture}
  \caption{This is a caption}
\end{figure}

\begin{figure}
  \centering
  \begin{tikzpicture}
    \begin{axis}[ybar stacked,bar width=5pt]
    \addplot coordinates {
(1, 25.66)
(2, 32.59)
(3, 35.77)
(4, 36.65)
(5, 25.37)
(6, 31.58)
(7, 34.19)
(8, 36.09)
(9, 25.42)
(10, 31.70)
(11, 34.03)
(12, 35.56)
(13, 28.66)
(14, 32.38)
(15, 33.93)
(16, 37.31)
(17, 26.26)
(18, 34.34)
(19, 35.18)
(20, 36.33)
(21, 31.12)
(22, 36.91)
(23, 38.96)
(24, 41.52)
(25, 31.35)
(26, 45.08)
(27, 46.56)
(28, 47.01)
};
    \addplot coordinates {
(1, 0.01)
(2, 0.75)
(3, 0.89)
(4, 0.93)
(5, 0.01)
(6, 0.96)
(7, 1.26)
(8, 1.34)
(9, 0.01)
(10, 1.49)
(11, 1.53)
(12, 1.98)
(13, 0.02)
(14, 1.67)
(15, 1.60)
(16, 2.45)
(17, 0.02)
(18, 1.59)
(19, 1.86)
(20, 2.23)
(21, 0.03)
(22, 1.74)
(23, 2.06)
(24, 2.18)
(25, 0.05)
(26, 2.31)
(27, 2.12)
(28, 2.32)
};
    \addplot coordinates {
(1, 0.59)
(2, 2.09)
(3, 4.30)
(4, 6.02)
(5, 1.31)
(6, 3.83)
(7, 7.17)
(8, 10.96)
(9, 2.08)
(10, 5.24)
(11, 11.38)
(12, 14.28)
(13, 2.59)
(14, 7.40)
(15, 13.45)
(16, 19.04)
(17, 3.66)
(18, 13.03)
(19, 23.48)
(20, 28.21)
(21, 8.68)
(22, 16.42)
(23, 34.34)
(24, 46.12)
(25, 11.02)
(26, 32.69)
(27, 60.49)
(28, 87.13)
};
    \addplot coordinates {
(1, 0.58)
(2, 4.77)
(3, 4.53)
(4, 4.35)
(5, 1.17)
(6, 2.75)
(7, 2.02)
(8, 2.28)
(9, 0.99)
(10, 1.40)
(11, 1.49)
(12, 1.57)
(13, 2.48)
(14, 1.72)
(15, 1.56)
(16, 1.78)
(17, 1.05)
(18, 1.33)
(19, 1.74)
(20, 1.80)
(21, 1.61)
(22, 1.75)
(23, 1.80)
(24, 1.95)
(25, 1.76)
(26, 2.02)
(27, 2.12)
(28, 2.15)
};
    \addplot coordinates {
(1, 0.00)
(2, 0.00)
(3, 0.00)
(4, 0.00)
(5, 0.00)
(6, 0.00)
(7, 0.00)
(8, 0.00)
(9, 0.00)
(10, 0.00)
(11, 0.00)
(12, 0.00)
(13, 0.00)
(14, 0.00)
(15, 0.00)
(16, 0.00)
(17, 0.00)
(18, 0.00)
(19, 0.00)
(20, 0.00)
(21, 0.00)
(22, 0.00)
(23, 0.00)
(24, 0.00)
(25, 0.00)
(26, 0.00)
(27, 0.00)
(28, 0.00)
};
    \addplot coordinates {
(1, 0.00)
(2, 0.03)
(3, 0.04)
(4, 0.05)
(5, 0.00)
(6, 0.04)
(7, 0.06)
(8, 0.08)
(9, 0.00)
(10, 0.14)
(11, 0.11)
(12, 0.19)
(13, 0.00)
(14, 0.57)
(15, 0.27)
(16, 0.47)
(17, 0.00)
(18, 0.34)
(19, 0.61)
(20, 0.52)
(21, 0.00)
(22, 0.64)
(23, 0.63)
(24, 0.96)
(25, 0.00)
(26, 0.78)
(27, 1.06)
(28, 1.49)
};
    \legend{Application,Memory Copies,High-level,Low-level,Mapper,System}
    \end{axis}
  \end{tikzpicture}
  \caption{This is a caption}
\end{figure}

>>>>

\section{Experiments}
\label{sec:exp}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The structure of the circuit simulator was presented in section~\ref{sec:ex}.
Our implementation uses CUDA to perform the computations on the GPU, and Legion
automatically handles the movement of data between the GPUs' memories and the
system memory, but only when necessary.  In fact, with the help of an
application-specific mapper, it is able to keep much of
the data permanently resident in a given GPU for the entirety of the simulation.
Figure~\ref{sfig:results1:perf} shows the relative speedup as the simulation is
spread over multiple nodes in the cluster.  The size of the circuit
being simulated is not changed as the node count increases.  This is therefore
a demonstration of ``strong scaling''.  Adding a second node to the simulation
speeds it up by 77\%, and with four nodes, the simulation is sped up by a total
of 216\% (i.e. a factor of 3.16x).

@@

\pgfplotsset{every axis legend/.append style={
  font=\tiny,
  at={(0.02,0.98)},
  anchor=north west}}

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% num gpus = 2
  (1, 1.99)
  (2, 3.46)
  (3, 3.44)
  (4, 5.90)
        };
        \addplot coordinates {
% num gpus = 1
  (1, 1.00)
  (2, 1.86)
  (3, 2.40)
  (4, 3.41)
        };
      \legend{2 GPU/node,1 GPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results1:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 106.892 & 105.387 & 1.578 & 0.003 & 21.624 & 0 & 0\\
 & $2$ & 57.388 & 105.407 & 10.348 & 0.003 & 15.177 & 0 & 0.001\\
 & $3$ & 44.552 & 105.41 & 11.935 & 0.003 & 11.695 & 0 & 0.002\\
 & $4$ & 31.368 & 105.42 & 12.875 & 0.004 & 8.419 & 0 & 0.003\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 53.787 & 105.397 & 1.857 & 0.004 & 10.953 & 0 & 0\\
 & $2$ & 30.923 & 105.415 & 10.716 & 0.004 & 7.937 & 0 & 0.002\\
 & $3$ & 31.037 & 105.414 & 12.558 & 0.004 & 7.996 & 0 & 0.001\\
 & $4$ & 18.103 & 105.42 & 13.747 & 0.004 & 4.638 & 0 & 0.003\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results1:timers}
  }
  \caption{Circuit Simulator Results}
\end{figure}

\pgfplotsset{every axis legend/.append style={
  font=\tiny,
  at={(0.02,0.98)},
  anchor=north west}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

The bar chart in figure~\ref{sfig:results2:timers} shows MORE STUFF.

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% 12 CPUs
  (1, 5.29)
  (2, 7.34)
  (3, 7.30)
  (4, 10.14)
        };
        \addplot coordinates {
% 6 CPUs
  (1, 4.51)
  (2, 6.00)
  (3, 6.57)
  (4, 8.83)
        };
        \addplot coordinates {
% 4 CPUs
  (1, 3.36)
  (2, 4.05)
  (3, 5.86)
  (4, 6.68)
        };
        \addplot coordinates {
% 3 CPUs
  (1, 2.58)
  (2, 3.55)
  (3, 4.35)
  (4, 5.61)
        };
        \addplot coordinates {
% 2 CPUs
  (1, 1.83)
  (2, 2.43)
  (3, 3.48)
  (4, 4.15)
        };
        \addplot coordinates {
% 1 CPUs
  (1, 1.00)
  (2, 1.61)
  (3, 1.87)
  (4, 2.33)
        };
      \legend{12 CPU/node,6 CPU/node,4 CPU/node,3 CPU/node,2 CPU/node,1 CPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results2:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 40.718 & 38.486 & 0.008 & 0.996 & 0.544 & 0 & 0\\
 & $2$ & 25.365 & 43.602 & 0.455 & 2.027 & 0.682 & 0 & 0.043\\
 & $3$ & 21.808 & 49.256 & 0.513 & 2.377 & 0.765 & 0 & 0.06\\
 & $4$ & 17.476 & 53.181 & 0.501 & 2.912 & 0.743 & 0 & 0.072\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 22.289 & 38.55 & 0.009 & 1.694 & 0.68 & 0 & 0\\
 & $2$ & 16.787 & 51.081 & 0.573 & 2.373 & 0.756 & 0 & 0.056\\
 & $3$ & 11.706 & 49.502 & 0.733 & 2.661 & 0.749 & 0 & 0.072\\
 & $4$ & 9.817 & 50.798 & 0.86 & 2.755 & 0.735 & 0 & 0.1\\
\midrule
\multirow{4}{*}{$3$} & $1$ & 15.799 & 38.507 & 0.01 & 2.056 & 0.765 & 0 & 0\\
 & $2$ & 11.462 & 48.698 & 0.951 & 2.682 & 0.819 & 0 & 0.109\\
 & $3$ & 9.363 & 50.786 & 1.282 & 2.976 & 0.767 & 0 & 0.081\\
 & $4$ & 7.26 & 51.778 & 1.285 & 3.172 & 0.818 & 0 & 0.117\\
\midrule
\multirow{4}{*}{$4$} & $1$ & 12.11 & 39.296 & 0.011 & 2.17 & 0.827 & 0 & 0\\
 & $2$ & 10.05 & 49.799 & 1.145 & 3.023 & 0.82 & 0 & 0.24\\
 & $3$ & 6.951 & 51.216 & 1.367 & 3.137 & 0.798 & 0 & 0.12\\
 & $4$ & 6.093 & 52.183 & 1.216 & 3.317 & 0.782 & 0 & 0.135\\
\midrule
\multirow{4}{*}{$6$} & $1$ & 9.031 & 40.265 & 0.013 & 2.536 & 0.969 & 0 & 0\\
 & $2$ & 6.79 & 48.992 & 0.946 & 3.182 & 0.937 & 0 & 0.145\\
 & $3$ & 6.199 & 51.904 & 1.061 & 3.752 & 0.909 & 0 & 0.185\\
 & $4$ & 4.612 & 52.603 & 1.238 & 3.712 & 0.872 & 0 & 0.222\\
\midrule
\multirow{4}{*}{$12$} & $1$ & 7.704 & 45.959 & 0.03 & 4.01 & 1.765 & 0 & 0\\
 & $2$ & 5.547 & 65.432 & 1.019 & 4.762 & 1.328 & 0 & 0.232\\
 & $3$ & 5.577 & 68.74 & 1.059 & 5.922 & 1.384 & 0 & 0.322\\
 & $4$ & 4.017 & 67.662 & 1.19 & 4.882 & 1.22 & 0 & 1.485\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results2:timers}
  }

  \caption{Fluid Results}
\end{figure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\begin{figure}
  \centering
  \subfigure[Performance Scaling]{
    \begin{tikzpicture}
      \begin{axis}[xlabel=Number of Nodes,ylabel=Normalized Speedup,height=5cm,width=8.5cm,xtick={1,2,3,4}]
        \addplot coordinates {
% num gpus = 2
  (1, 1.99)
  (2, 3.46)
  (3, 3.44)
  (4, 5.90)
        };
        \addplot coordinates {
% num gpus = 1
  (1, 1.00)
  (2, 1.86)
  (3, 2.40)
  (4, 3.41)
        };
      \legend{2 GPU/node,1 GPU/node}
      \end{axis}
    \end{tikzpicture}
    \label{sfig:results3:perf}
  }

  \subtable[Execution Time Breakdown]{
   \tiny
    \begin{tabular}{c@{\hspace{2pt}}cD{.}{.}{3}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}@{\hspace{2pt}}D{.}{.}{3}}
\toprule
GPUs/ & \# \\
node & nodes & \multicolumn{1}{c}{Wall Clock} & \multicolumn{1}{c}{Application} & \multicolumn{1}{c}{Copies} & \multicolumn{1}{c}{High-level} & \multicolumn{1}{c}{Low-level} & \multicolumn{1}{c}{Mapper} & \multicolumn{1}{c}{System} \\
\midrule
\multirow{4}{*}{$1$} & $1$ & 106.892 & 105.387 & 1.578 & 0.003 & 21.624 & 0 & 0\\
 & $2$ & 57.388 & 105.407 & 10.348 & 0.003 & 15.177 & 0 & 0.001\\
 & $3$ & 44.552 & 105.41 & 11.935 & 0.003 & 11.695 & 0 & 0.002\\
 & $4$ & 31.368 & 105.42 & 12.875 & 0.004 & 8.419 & 0 & 0.003\\
\midrule
\multirow{4}{*}{$2$} & $1$ & 53.787 & 105.397 & 1.857 & 0.004 & 10.953 & 0 & 0\\
 & $2$ & 30.923 & 105.415 & 10.716 & 0.004 & 7.937 & 0 & 0.002\\
 & $3$ & 31.037 & 105.414 & 12.558 & 0.004 & 7.996 & 0 & 0.001\\
 & $4$ & 18.103 & 105.42 & 13.747 & 0.004 & 4.638 & 0 & 0.003\\
\bottomrule \\
    \end{tabular}
    \label{sfig:results3:timers}
  }
  \caption{Tree Search Results}
\end{figure}

### 2011-11-06 doc/pldi2012/highlevel.tex
several figures done - references linked up

\subsubsection{Putting It All Together: Circuit Example}
\label{subsec:cirdependence}
To illustrate concretely how dependence analysis works, we describe the steps for
performing dependence analysis for running circuit example.  When the {\tt simulate\_circuit}
task begins executing there are two region trees rooted at the logical
regions for {\tt all\_nodes} and {\tt all\_wires}.  For conciseness we will only
show the region tree for {\tt all\_nodes}.  At the start of the task, there exists
a single abstract instance at the root node representing the valid set of physical
instances from which sub tasks will be allowed to pull data.  The state of the
system at this point can be observed in figure \ref{fig:circdep1}.

When each of the {\tt compute\_new\_current} tasks are issued they must perform dependence
analysis for two node regions.  In the {\tt private\_node} case they will first open
up the {\tt p\_nodes\_pvs} partition and then open up the {\tt p\_pvt\_nodes} sub partition
for each of their subregions.  Since all of the private regions use a different subregion
of a disjoint partition for the private node accesses, no dependence is detected.  Similarly,
when all the dependence analysis is performed for the {\tt p\_ghost\_nodes} subregions,
each of the necessary partitions are opened.  There is no dependence with any of the private
nodes since all the ghost nodes traverse a different sub region of the disjoint partition
{\tt p\_nodes\_pvs}.  There is also no dependence between any tasks even though the
{\tt p\_ghost\_nodes} partition is aliased because all the ghost accesses are read-only.
The state of the region tree after dependence analysis has been performed for the
{\tt compute\_new\_current} nodes can be seen in figure \ref{fig:circdep2}.

In the second phase of the computation, all of the {\tt distribute\_charge} tasks
will be issued.  For these tasks they will first analyze traverse the region tree
for their subregions containing their private nodes.  The path to these regions are
already open, but when the dependence analysis arrives at the specific private node subregion it will
discover a dependence between the task and the {\tt compute\_new\_currents} task that operated
on that region previously.  This dependence will be recorded and the 
{\tt distribute\_charge} task will be made the new active task as it dominated the
previous task.  For the ghost node regions, the dependence analysis will discover that the
there is a dependence between each of the {\tt distribute\_charge} tasks and all of the
{\tt compute\_new\_current} tasks because the {\tt distribute\_charge} tasks are
performing writes and the partition is aliased.  However, the runtime will detect this as
anti-dependences which are resolved by forcing the {\tt distribute\_charge} tasks to
create new valid abstract instances rather than use the same abstract instances as
each of the {\tt compute\_new\_current} tasks.  There are no dependences detected
between each of the {\tt distribute\_charge} tasks on the ghost regions because
the {\tt Simultaneous} coherence property permits multiple tasks to be using the same
partition at the same time even if the subregions they are accessing are aliased.  The
state of the region tree after dependence analysis for {\tt distribute\_charge} can
be seen in figure \ref{fig:circdep3}.

>>>>

\subsubsection{Putting It All Together: Circuit Example}
\label{subsec:cirdependence}
To illustrate concretely how dependence analysis works, we describe the steps for
performing dependence analysis for running circuit example.  When the {\tt simulate\_circuit}
task begins executing there are two region trees rooted at the logical
regions for {\tt all\_nodes} and {\tt all\_wires}.  For conciseness we will only
show the region tree for {\tt all\_nodes}.  At the start of the task, there exists
a single abstract instance at the root node representing the valid set of physical
instances from which sub tasks will be allowed to pull data.  The state of the
system at this point can be observed in figure~\ref{sfig:mapping_fig:cnc}.

When each of the {\tt compute\_new\_current} tasks are issued they must perform dependence
analysis for two node regions.  In the {\tt private\_node} case they will first open
up the {\tt p\_nodes\_pvs} partition and then open up the {\tt p\_pvt\_nodes} sub partition
for each of their subregions.  Since all of the private regions use a different subregion
of a disjoint partition for the private node accesses, no dependence is detected.  Similarly,
when all the dependence analysis is performed for the {\tt p\_ghost\_nodes} subregions,
each of the necessary partitions are opened.  There is no dependence with any of the private
nodes since all the ghost nodes traverse a different sub region of the disjoint partition
{\tt p\_nodes\_pvs}.  There is also no dependence between any tasks even though the
{\tt p\_ghost\_nodes} partition is aliased because all the ghost accesses are read-only.
The state of the region tree after dependence analysis has been performed for the
{\tt compute\_new\_current} nodes can be seen in figure~\ref{sfig:mapping_fig:dc}.

In the second phase of the computation, all of the {\tt distribute\_charge} tasks
will be issued.  For these tasks they will first analyze traverse the region tree
for their subregions containing their private nodes.  The path to these regions are
already open, but when the dependence analysis arrives at the specific private node subregion it will
discover a dependence between the task and the {\tt compute\_new\_currents} task that operated
on that region previously.  This dependence will be recorded and the 
{\tt distribute\_charge} task will be made the new active task as it dominated the
previous task.  For the ghost node regions, the dependence analysis will discover that the
there is a dependence between each of the {\tt distribute\_charge} tasks and all of the
{\tt compute\_new\_current} tasks because the {\tt distribute\_charge} tasks are
performing writes and the partition is aliased.  However, the runtime will detect this as
anti-dependences which are resolved by forcing the {\tt distribute\_charge} tasks to
create new valid abstract instances rather than use the same abstract instances as
each of the {\tt compute\_new\_current} tasks.  There are no dependences detected
between each of the {\tt distribute\_charge} tasks on the ghost regions because
the {\tt Simultaneous} coherence property permits multiple tasks to be using the same
partition at the same time even if the subregions they are accessing are aliased.  The
state of the region tree after dependence analysis for {\tt distribute\_charge} can
be seen in figure~\ref{sfig:mapping_fig:volt}.
